Verification of Stencil Computations through Spatial Specifications

### 2016-07-07 paper.tex
Gather lines into same line

As another example, the following
implements and specifies the \emph{Roberts cross}
edge-detection convolution~\cite{davis1975survey}:
%%
\begin{minted}[breakindent=5.5em]{fortran}
do j=0, jmax-1
    do i=0, imax-1
      x = a(i,j) - a(i+1,j+1)
      y = a(i+1,j) - a(i,j+1)
      != stencil forward(depth=1,dim=1) * forward(depth=1,dim=2) :: a
      b(i,j) = sqrt(x*x+y*y)
   end do
end do
\end{minted}

@@

We demonstrate the inference procedure over the
following example program which computes the mean value
of a five-point stencil:%at each index of the input array:
%%
\begin{minted}{fortran}
do i = 1, (n-1)
   do j = 1, (m-1)
      x       = a(i-1, j) + a(i+1, j)
      y       = a(i, j-1) + a(i, j+1)
      b(i, j) = (a(i, j) + x + y) / 5.0
   end do
end do
\end{minted}
%%
\subsubsection{Step 1: Standard control and data-flow analyses}
\label{sec:inf-step1}

@@

\begin{example}
We give an extended example of verifying a stencil computation against
its specification. We consider a more general, but still consistent, version of the \textit{five-point}
stencil specification inferred previously in
Section~\ref{subsec:inference} (see top-left):
%
\begin{minted}[breakindent=8.1em]{fortran}
!= region fivepoint = centered(depth=1,dim=1) + centered(depth=1,dim=2)
!= stencil readOnce, fivepoint :: b
a(i,j) = b(i,j-1) + b(i,j) + b(i,j+1) + b(i-1,j) + b(i+1,j)
\end{minted}
%
We refer to the assignment on line three as $l3$ for brevity.

>>>>

As another example, the following
implements and specifies the \emph{Roberts cross}
edge-detection convolution~\cite{davis1975survey}:
%%
\begin{minted}[breakindent=5.5em]{fortran}
do j=0, jmax-1
  do i=0, imax-1
    x = a(i,j)-a(i+1,j+1); y = a(i+1,j)-a(i,j+1)
    != stencil forward(depth=1,dim=1) * forward(depth=1,dim=2) :: a
    b(i,j) = sqrt(x*x+y*y)
  end do
end do
\end{minted}

@@

We demonstrate the inference procedure over the
following example program which computes the mean value
of a five-point stencil:%at each index of the input array:
%%
\begin{minted}{fortran}
do i = 1, (n-1)
  do j = 1, (m-1)
    x = a(i-1, j)+a(i+1, j); y = a(i, j-1)+a(i, j+1)
    b(i, j) = (a(i, j) + x + y) / 5.0
  end do
end do
\end{minted}
%%
\subsubsection{Step 1: Standard control and data-flow analyses}
\label{sec:inf-step1}

@@

\begin{example}
We give an extended example of verifying a stencil computation against
its specification. We consider a more general, but still consistent, version of the \textit{five-point}
stencil specification inferred previously in
Section~\ref{subsec:inference} (see top-left):
%
\begin{minted}[breakindent=8.1em]{fortran}
!= region fivepoint = centered(depth=1,dim=1) + centered(depth=1,dim=2)
!= stencil readOnce, fivepoint :: b
a(i,j) = b(i,j-1)+b(i,j)+b(i,j+1)+b(i-1,j)+b(i+1,j)
\end{minted}
%
We refer to the assignment on line three as $l3$ for brevity.
